Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
Summarize list of tasks.

>>>>

We will divide our participants into treatments
by censorship environment.
All participants will be asked to complete the same
list of tasks.
We constructed the list by looking at some of the top
Alexa sites and imagining what might be reasonable
and relevant tasks for each
(that do not require a participant to reveal private information
like passwords).
The tasks are not all intended to be challenging to complete.
Some may not even require the use of Tor Browser,
depending on the censorship environment in effect.

\begin{itemize}
\item Do a Google web search.
\item Watch a YouTube video.
\item Find the Amazon best-selling books.
\item Find Yahoo's exchange rate between dollars and euros.
\item Read the Wikipedia featured article.
\item Find the Twitter trending topics.
\item Find directions on Bing Maps.
\end{itemize}
